Coalescent inference of mutation spectrum histories from sample frequency spectra

### 2019-09-03 manuscript/main.tex
more verbose conditioning

\author{
W. DeWitt$^{1}$, K. Decker Harris$^{2,3}$, and K. Harris$^{1}$\\
{\small
$^1$Genome Sciences,
$^2$Paul G.\ Allen School of Computer Science \& Engineering, 
and $^3$Biology}\\
{\small University of Washington, Seattle, USA}
% \small{$^\ast$ Equal contribution}
}

@@

In linkage equilibrium the log likelihood function of the mutation intensity history $\boldsymbol z$ given an observed SFS vector $\boldsymbol x = (x_1,\dots,x_{n-1})$ and demographic history $\boldsymbol y$ is given by the Poisson random field approximation \citep{}
\[
\ell(\boldsymbol z; \boldsymbol x, \boldsymbol y) = \boldsymbol x^\intercal\log(L_{n, \boldsymbol y} \boldsymbol z) - \boldsymbol 1^\intercal L_{n, \boldsymbol y} \boldsymbol z,
\]
where $\log(\cdot)$ operates elementwise, and we've dropped a constant term wrt $\boldsymbol z$.

@@

The \texttt{mushi} software package is available at \url{https://github.com/harrispopgen/mushi}.
%WD cite whatever packages we use, e.g. proxtv

>>>>

\author{
W.S. DeWitt$^{1,4}$, K. Decker Harris$^{2,3}$, and K. Harris$^{1}$\\
{\small
$^1$Department of Genome Sciences,
$^2$Paul G.\ Allen School of Computer Science \& Engineering,}\\
{\small and $^3$Department of Biology, University of Washington, Seattle, WA}\\
{\small $^4$Computational Biology Program, Fred Hutchinson Cancer Research Center, Seattle, WA}
% \small{$^\ast$ Equal contribution}
}

@@

In linkage equilibrium the log likelihood function of the mutation intensity history $\boldsymbol z$ given an observed SFS vector $\boldsymbol x = (x_1,\dots,x_{n-1})$ and demographic history $\boldsymbol y$ is given by the Poisson random field approximation \citep{}
\[
\ell(\boldsymbol z; \boldsymbol x, \boldsymbol y, n) = \boldsymbol x^\intercal\log(L_{n, \boldsymbol y} \boldsymbol z) - \boldsymbol 1^\intercal L_{n, \boldsymbol y} \boldsymbol z,
\]
where $\log(\cdot)$ operates elementwise, and we've dropped a constant term wrt $\boldsymbol z$.

@@

The \texttt{mushi} software package is available at \url{https://github.com/harrispopgen/mushi}.
%WD cite whatever packages we use, e.g. proxtv, msprime, stdpopsim, etc.
